Epistemic Logics For Knowledge Bases

### 2010-12-15 lattice_justification.tex
Added todonotes

{\color{red} NOTE.  THIS SECTION HAS SOME SERIOUS PROBLEMS AND IT'S PROBABLY
WRONG...}

Implicit in our previous presentation of SJL.  $\oplus$ behaves like a union
operation for knowledge bases, and dually like an intersection operation on
accessibility relations.  It is natural to think of $\oplus$ as a join/meet
operator over a {\tmem{semi-lattice}}.  In this section we make this
explicit, by increasing the expressive power of simple JL to express the order
theory inherent in knowledge bases.  We call the novel logic presented in
this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
however we have decided to shorten semic-lattice to lattice in this article
for purposes of concision.}}.  Lattice JL may be considered a novel logic for
studying the dynamics of \tmtextit{theory change}, where the logic employed by
the changing theories could be LJL itself.

>>>>

Implicit in our previous presentation of SJL is the following
principle: 
\todo[noline]{THIS SECTION IS  PROBABLY WRONG}
 $\oplus$ behaves like a union
operation for knowledge bases, and dually like an intersection operation on
accessibility relations.  It is natural to think of $\oplus$ as a join/meet
operator over a {\tmem{semi-lattice}}.  In this section we make this
explicit, by increasing the expressive power of simple JL to express the order
theory inherent in knowledge bases.  We call the novel logic presented in
this section \tmtextit{Lattice Justification Logic} (LJL){\footnote{We note
that ``Semi-Lattice Justification Logic'' may be a more appropriate name,
however we have decided to shorten semic-lattice to lattice in this article
for purposes of concision.}}.  Lattice JL may be considered a novel logic for
studying the dynamics of \tmtextit{theory change}, where the logic employed by
the changing theories could be LJL itself.
